Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Corrected abstract and title, @unintendedbear check it out

\title{Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System}

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and their Chief Security Officers (CSOs) particularly, want to be sure that their Security Policies are complied. This goal turned hard to achieve since employees are able to use their own devices (laptops, smartphones, and tablets) at work, or at home but for work purposes. As this is part of the Bring Your Own Device (BYOD) philosophy and is being adopted by many companies everyday, a number of solutions have arisen in order to adapt it securely. In this paper, a novel system to deal with this situation is introduced, named  MUSES (Multiplatform Usable Endpoint Security). It is a system able to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, still in development, is compared with the most relevant solutions offered by other companies to deal with the same issues as MUSES, remarking the advantages that our system will offer with respect to them.
\end{abstract}

>>>>

\title{Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System}

@@

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   ABSTRACT   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{abstract} 
Enterprises, and particularly their Chief Security Officers (CSOs),
want to ensure that their Security Policies are complied, but this
goal turned hard to achieve since employees are able to use, or bring
their own devices (in what is known as BYOD, bring your own device) at
work, or at home but for work purposes. As this BYOD philosophy is
adopted by many companies everyday, a number of solutions have arisen
in order to adopt it securely. In this paper, a novel system named
MUSES (Multiplatform Usable Endpoint Security) which should be able 
to adapt Security Policies to a BYOD environment is introduced. MUSES
has been designed to cope with security issues regarding the enterprise security policies, but as a user-centric tool, which considers system user's behaviour in order to adapt, improve, or even increase the defined set of security rules. MUSES applies machine learning and computational intelligence techniques in order to do this, and also would be able to predict future security incidences produced by these users.
This system, still in development, is compared with the most relevant
solutions offered by other companies to deal with the same issues as
MUSES, remarking the advantages that our system will offer with
respect to them. % What do we do in this paper? Present the
                 % architecture? The prototypes? - JJ
\end{abstract}
